PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-04-13 txt/manuscript_short.tex
Update short manuscript and supplemental material

@@

In this section, we describe how the benchmarking process in PyQBench works. We start by
discussing necessary mathematical preliminaries. Then, we present the general form of the
discrimination scheme used in PyQBench and practical considerations on how to implement it taking
into account the limitations of the current NISQ devices.

@@

Unsurprisingly, both the $\ket{\psi_0}$ and the final measurements $\mathcal{P}_{V_i}$ have to be
chosen specifically for given $U$ to maximize the probability of a correct guess. The detailed
description how these choices are made in \cite{watrous}, and for now we will focus only how this
scheme can be implemented on the actual devices, assuming that all the components are known.

@@

The PyQBench library also contains a readily available implementation of all necessary components
needed to run discrimination experiments for parametrized Fourier family of measurements (see
\cite{appendix}). However, if one only wishes to use this particular family of measurements in their
benchmarks, then using PyQBench as a command line tool might be more straightforward. PyQBench's
command line interface allows running the benchmarking process without writing Python code. The
configuration of CLI is done by YAML \cite{yaml} files describing the benchmark to be performed and
the description of the backend on which the benchmark should be run. The same benchmark can be used
with different backends and vice versa.

@@

\section{Illustrative examples}
\label{sec:examples} In this section, we present two examples demonstrating the usage of PyQBench.
In the first example, we show how to implement a discrimination scheme for a user--defined
measurement and possible ways of using this scheme with \texttt{qbench} library. The second example
demonstrates the usage of the CLI. We show how to prepare the input files for the benchmark and how
to run it using the \texttt{qbench} tool.

\subsection{Using \texttt{qbench} CLI}
Using PyQBench as a library allows one to conduct a two--qubits benchmark with arbitrary von Neumann
measurement. However, as discussed in the previous guide, it requires writing some amount of code.
For a Fourier parametrized family of measurements, PyQBench offers a simplified way of conducting
benchmarks using a Command Line Interface (CLI). The workflow with PyQBench's CLI can be summarized
as the following list of steps:

@@

For the synchronous experiment, the part of output looks similar to the one below. The whole YAML
file can be seen in \ref{app:example}.
%Consider the particular experiment data
\begin{lstlisting}[language=Python]
data:
- target: 0
  ancilla: 1
  phi: 0.0
  results_per_circuit:
  - name: id
  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
  mitigation_info:
	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
\end{lstlisting}

@@

\subsubsection{Computing probabilities}
As a last step in the processing workflow, the results file has to be passed to \texttt{tabulate}
command:
\begin{lstlisting}[language=Python]
qbench disc-fourier tabulate results.yml results.csv
\end{lstlisting}
A sample CSV file is provided below:
\begin{table}[ht!]
\begin{center}
	\begin{tabular}{|c c c c c c|} 
		\hline
		target & ancilla & phi & ideal$\_$prob  & disc$\_$prob & mit$\_$disc$\_$prob \\ [0.5ex] 
		\hline\hline
		0 & 1 & 0 & 0.5 & 0.46 & 0.45  \\ 
		\hline
		0 & 1 & 3.14 & 1 & 0.95 & 0.98  \\
		\hline
		0 & 1 & 6.28 & 0.5 & 0.57 & 0.58  \\
		\hline
		1 & 2 & 0 & 0.5  & 0.57 & 0.57 \\
		\hline
		1 & 2 & 3.14 & 1 & 0.88 & 0.94  \\ 
		\hline
		1 & 2 & 6.28 & 0.5 & 0.55 & 0.56  \\ 
		\hline
	\end{tabular}
\caption{The resulting CSV file contains table with columns \texttt{target}, \texttt{ancilla}, \texttt{phi},
	\texttt{ideal\_prob}, \texttt{disc\_prob} and, optionally, \texttt{mit\_disc\_prob}. Each row in the
	table describes results for a tuple of \texttt{(target, ancilla, phi)}.  The reference optimal value
	of discrimination probability is present in \texttt{ideal\_prob} column, whereas the obtained,
	empirical discrimination probability can be found in the \texttt{disc\_prob} column. The
	\texttt{mit\_disc\_prob} column contains empirical discrimination probability after applying the
	\texttt{Mthree} error mitigation \cite{mthree, mthreepublication}, if it was applied.}
\label{fig:tabulateresults}
\end{center}
\end{table}

@@

In this study, we develop a Python library PyQBench, an innovative open-source framework for
benchmarking gate-based quantum computers.

%%%%%%%%%%%%%%
PyQBench can benchmark NISQ devices by verifying their capability of discriminating between two von
Neumann measurements. PyQBench offers a simplified, ready-to-use, command line interface (CLI) for
running benchmarks using a predefined parameterized Fourier family of measurements. For more
advanced scenarios, PyQBench offers a way of employing user-defined measurements instead of
predefined ones.
\section{Conflict of Interest}
We wish to confirm that there are no known conflicts of interest associated with this publication
and there has been no significant financial support for this work that could have influenced its
out- come.

>>>>

\usepackage{xr}
\externaldocument{supplemental}

@@

In this section, we describe how the benchmarking process in PyQBench works. We start by
discussing necessary mathematical preliminaries. Then, we present the general form of the
discrimination scheme used in PyQBench and practical considerations on how to implement it taking
into account the limitations of the current NISQ devices. We encourage the readers interested
in a more in--depth discussion of the mathematical foundations behind our discrimination scheme to read
Section \ref{app:preliminaries} in the supplemental materials.

@@

@@

The PyQBench library also contains a readily available implementation of all necessary components
needed to run discrimination experiments for parametrized Fourier family of measurements (see
Section \ref{app:optimal-probability} in supplemental material). However, if one only wishes to use
this particular family of measurements in their benchmarks, then using PyQBench as a command line tool
might be more straightforward. PyQBench's command line interface allows running the benchmarking process
without writing Python code. The configuration of CLI is done by YAML \cite{yaml} files describing the
benchmark to be performed and the description of the backend on which the benchmark should be run.
The same benchmark can be used with different backends and vice versa.

@@

\section{Illustrative examples}
\label{sec:examples} In this section, we demonstrate the usage of PyQBench.
For brevity, we decided to present only the usage of the CLI tool, as it is likely to be the most
popular use case. We refer readers interested in implementing their discrimination schemes using
custom measurements to PyQBench's documentation \cite{pyqbenchdocs}, where we describe the whole
process, and to the Section \ref{app:hadamard} in the supplemental material, where we discuss
the relevant mathematical details.

\subsection{Using \texttt{qbench} CLI}
PyQBench offers a simplified way of conducting benchmarks using a Command Line Interface (CLI).
The workflow with PyQBench's CLI can be summarized as the following list of steps:

@@

For the synchronous experiment, the part of the output looks similar to the one below. The whole YAML
file can be seen in Section \ref{app:example.} in the supplemental material.
%Consider the particular experiment data
\begin{lstlisting}[language=Python]
data:
- target: 0
  ancilla: 1
  phi: 0.0
  results_per_circuit:
  - name: id
  histogram: {'00': 28, '01': 26, '10': 21, '11': 25}
  mitigation_info:
	target: {prob_meas0_prep1: 0.052200000000000024, prob_meas1_prep0: 0.0172}
	ancilla: {prob_meas0_prep1: 0.05900000000000005, prob_meas1_prep0: 0.0202}
  mitigated_histogram: {'00': 0.2637212373658018, '01': 0.25865061319892463, '10': 0.2067279352110304, '11': 0.2709002142242433}
\end{lstlisting}

@@

\subsubsection{Computing probabilities}
As a last step in the processing workflow, the results file has to be passed to \texttt{tabulate}
command:
\begin{lstlisting}[language=Python]
qbench disc-fourier tabulate results.yml results.csv
\end{lstlisting}
A sample CSV file is provided in Table \ref{fig:tabulateresults}.
\begin{table}[ht!]
\begin{center}
	\begin{tabular}{|c c c c c c|} 
		\hline
		target & ancilla & phi & ideal$\_$prob  & disc$\_$prob & mit$\_$disc$\_$prob \\ [0.5ex] 
		\hline\hline
		0 & 1 & 0 & 0.5 & 0.46 & 0.45  \\ 
		\hline
		0 & 1 & 3.14 & 1 & 0.95 & 0.98  \\
		\hline
		0 & 1 & 6.28 & 0.5 & 0.57 & 0.58  \\
		\hline
		1 & 2 & 0 & 0.5  & 0.57 & 0.57 \\
		\hline
		1 & 2 & 3.14 & 1 & 0.88 & 0.94  \\ 
		\hline
		1 & 2 & 6.28 & 0.5 & 0.55 & 0.56  \\ 
		\hline
	\end{tabular}
\caption{The resulting CSV file contains table with columns \texttt{target}, \texttt{ancilla}, \texttt{phi},
	\texttt{ideal\_prob}, \texttt{disc\_prob} and, optionally, \texttt{mit\_disc\_prob}. Each row in the
	table describes results for a tuple of \texttt{(target, ancilla, phi)}.  The reference optimal value
	of discrimination probability is present in \texttt{ideal\_prob} column, whereas the obtained,
	empirical discrimination probability can be found in the \texttt{disc\_prob} column. The
	\texttt{mit\_disc\_prob} column contains empirical discrimination probability after applying the
	\texttt{Mthree} error mitigation \cite{mthree, mthreepublication}, if it was applied.}
\label{fig:tabulateresults}
\end{center}
\end{table}

@@

In this paper, we presented a Python library PyQBench, an innovative open-source framework for
benchmarking gate-based quantum computers.
PyQBench can benchmark NISQ devices by verifying their capability of discriminating between two von
Neumann measurements. PyQBench offers a simplified, ready-to-use, command line interface (CLI) for
running benchmarks using a predefined parameterized Fourier family of measurements. For more
advanced scenarios, PyQBench offers a way of employing user-defined measurements instead of
predefined ones.

\section{Conflict of Interest}
We wish to confirm that there are no known conflicts of interest associated with this publication
and there has been no significant financial support for this work that could have influenced its
out- come.
